---
title: "Reproducible document"
author: "TSK"
format: html
---


## Setup code chunk

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
?colnames
help(colnames)
theme(axis)
```


## About me


- Tine Storebjerg Knudsen
- Affiliations: SDCA, AU


My *research area* is **Diabetes and pregnancy**.

## Simple code
```{r}
3 * 3
```



## Basics of R

```{r}
1 + 1
```

## Setup code chunk


## Showing the data

```{r}
post_meal_data
```
```{r}
glimpse(post_meal_data)
```


## Testing for git

The weather is nice today

## Day 2 - code along

```{r hello}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

@fig-bmi-histo

## 9.5 exercise discrete plot

```{r}
#| fig-cap: "glykemi"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group-bar above for a cool plot!

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = glykemi)) +
  geom_bar()
```
```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Putting two plots side by side

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

```{r side-by-side-figs}
#| label: fig-bmi-glykemi
#| fig-cap: "BMI and glykemi, side-by-side"
#| fig-subcap:
#| - "Distribution of BMI"
#| - "Number of those with glykemi"
#| layout-ncol: 2

ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## 9.11 plotting two continuous variables

```{r}
#| fig-cap: "scatterplot showing BMI against AUC of p-glucose"
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() + 
  geom_smooth()
```

## collaborating with GitHub

